A Survey of Scientific Workflow Management Systems

### 2014-05-19 paper.tex
Makeflow text

Taverna is a flexible and extendible workflow environment
\cite{missier-soiland-reyes-etal:2010,sroka2009a} in that extending the
engine's functionality is facilitated through a Service Provider Interface
(SPI). The Taverna engine implements a sophisticated mechanism for enactment of
parallel workflows. These mechanisms manifest in the form of complex pipelines
and an advanced superpipelined enactment of workflows. Such a mechanism induces
multiple downstream workflow processors running in parallel for a dataset. In
the case of superpipelines, multiple pipeline instances run for multi-datasets
providing a high degree of parallelism limited only by the availability of
underlying resources. Taverna is not natively interfaced with external
computational infrastructure but the same can be achieved with the help of
extending the engine through one of its
SPIs~\cite{maheshwari-missier-etal:2009}. Recent implementations of Taverna
offers a client-server based environment in which a Taverna server can remotely
serve the workflow composition and execution services. This mode is useful in
the cloud computing environments where the server decides where to run the
Taverna services in the cloud.

@@

MOTEUR has sophisticated language-level expressions for data management
mechanisms within a workflow definition. It provides a diverse set of
parallel iterators that are well adapted for different combinations of input datasets
at the processor. An iteration strategy allows different combinations of the
data arriving at a processor along its multiple inputs. Running legacy
application code on distributed systems has been eased by MOTEUR by providing a
generic grid-service wrapper for these applications
\cite{glatard-montagnat-etal:2008a}. Services thus created can be readily
deployed by the MOTEUR runtime. MOTEUR workflows are written in the scufl
language and are compatible with those written for the Taverna SWE. It also
supports an extension of scufl language called the Gwendia~\cite{gwendia}
language, developed at the same laboratory. 
%
\paragraph{Makeflow} A make-like workflow platform~\cite{makeflow}.

>>>>

Taverna is a flexible and extendible workflow environment
\cite{missier-soiland-reyes-etal:2010,sroka2009a} in that extending the
engine's functionality is facilitated through a Service Provider Interface
(SPI). The Taverna engine implements a sophisticated mechanism for enactment of
parallel workflows. These mechanisms manifest in the form of complex pipelines
and an advanced superpipelined enactment of workflows. Such a mechanism induces
multiple downstream workflow processors running in parallel for a dataset. In
the case of superpipelines, multiple pipeline instances run for multi-datasets
providing a high degree of parallelism limited only by the availability of
underlying resources. Taverna is not natively interfaced with external
computational infrastructure but the same can be achieved with the help of
extending the engine through one of its
SPIs~\cite{maheshwari-missier-etal:2009}. In a crucial development, recent
implementations of Taverna offers a client-server based environment in which a
Taverna \emph{server} can remotely serve the workflow composition and execution
services. This mode is useful in the cloud computing environments where the
server decides where to run the Taverna services in the cloud.

@@

MOTEUR has sophisticated language-level expressions for data management
mechanisms within a workflow definition. It provides a diverse set of
parallel iterators that are well adapted for different combinations of input datasets
at the processor. An iteration strategy allows different combinations of the
data arriving at a processor along its multiple inputs. Running legacy
application code on distributed systems has been eased by MOTEUR by providing a
generic grid-service wrapper for these applications
\cite{glatard-montagnat-etal:2008a}. Services thus created can be readily
deployed by the MOTEUR runtime. MOTEUR workflows are written in the scufl
language and are compatible with those written for the Taverna SWE. It also
supports an extension of scufl language called the Gwendia~\cite{gwendia}
language, developed at the same laboratory. 
%
\paragraph{Makeflow} Makeflow~\cite{makeflow} is a make-like workflow platform.
Makeflow addresses the often-encountered problem of software and library
dependencies on workflow tasks execution for heterogeneous environments.
Makeflow offers techniques to ``link" and package the application execution
elements such as executables, libraries and configuration parameters.
